---
title: "Layout"
author: "Agda Loureiro"
date: "6/11/2020"
output: html_document
---

```{r}
pacman::p_load(ggsn, ggplot2, sf,raster)
```

Openning data


the interpolated data

```{r}
idw = raster("../deterministic-interpolation/maps/z_interpolated_idw.tif")
idw.df = as.data.frame(idw, xy = T)
idw.df = dplyr::rename(idw.df, z =  z_interpolated_idw)

krigagem = raster("../gstat/maps/z_interpolated.tif")
krig.df = as.data.frame(krigagem, xy = T)
krig.df = dplyr::rename(krig.df, z = z_interpolated)
```

the boundary

```{r}
contorno <- shapefile("../deterministic-interpolation/data/boundary/cotorno.shp")

#And then we create a grid

r = raster::raster(contorno, res = 10) #  "res" sets pixel resolution

rp = raster::rasterize(contorno, r, 0) 

grid = as(rp, "SpatialPixelsDataFrame") 

sp::plot(grid)

```

Plotting the map with sp

First we insert our interpolated data into our grid and transform it into a sf object
```{r}
library(sf)
grid$idw = idw.df$z
grid$krigagem = krig.df$z
grid = st_as_sf(grid)
grid
```
Plot simples 

```{r}
plot(grid[c("idw", "krigagem")])
```


We can also use ggplot2 library

```{r}
# esquisse::esquisser()
library(ggplot2)
library(ggspatial)
library(viridis)

idw = ggplot(grid) +
 aes(colour = idw) +
 geom_sf(size = 1L) +
  annotation_scale(location = "br", width_hint = 0.5, style = "bar") +
    coord_sf(xlim = c(-180, 1500), ylim = c(-180, 1550), expand = T,datum = sf::st_crs(32722), label_graticule = waiver(),   clip = "on") +
    xlab("Longitude") +
   ylab("Latitude") + 
 scale_color_viridis_c(option = "viridis") +
 theme_bw()

krigagem = ggplot(grid) +
 aes(colour = krigagem) +
 geom_sf(size = 1L) +
  annotation_scale(location = "br", width_hint = 0.5, style = "bar") +
    coord_sf(xlim = c(-180, 1500), ylim = c(-180, 1550), expand = T,datum = sf::st_crs(32722), label_graticule = waiver(),   clip = "on") +
    xlab("Longitude") +
   ylab("Latitude") + 
 scale_color_viridis_c(option = "viridis") +
 theme_bw()


```

```{r}
library(cowplot)
plot_grid(idw, krigagem, labels = "AUTO")
```


```{r}
library(ggpubr)
ggarrange(idw,krigagem, 
          labels = "AUTO",
          ncol = 2,
          nrow = 1,  
          align = "hv",
          common.legend = TRUE)
```

spplot

We can change intervals with sp package
 - para esse pacote utilizamos os mapas empilhados no formato raster
```{r}
maps = stack(idw, krigagem)
names(maps) = c("IDW", "OK")
```

```{r}
library(colormap)
viridis_colors <- colormap_pal(alpha = 1,
                               colormap = colormaps$viridis,
                               reverse = FALSE)
```

```{r}
spplot(maps, colorkey=list(space="right"), col.regions= viridis_colors)
layout.scale.bar(height = 1)
```

Or RasterVis 

 
 
```{r}
# devtools::install_github('oscarperpinan/rasterVis')
library(rasterVis)
library(lattice)
pacman::p_load(mapmisc)
```

```{r}
my.at <- c(0, seq (0.2, 1.7, by = 0.2), seq(1.7,5, by=1))
levelplot(maps, at=my.at)
```

```{r}
myColorkey <- list(at=my.at, ## where the colors change
                   labels=list(
                     at=my.at ## where to print labels
                     ))
levelplot(maps, at=my.at, colorkey=myColorkey)
```

```{r}
library(viridis)
## Customizing axis and title labels
levelplot(maps, margin=FALSE,
          names.attr=c('IDW', 'Krigagem'),
          at=my.at, colorkey=myColorkey,
          par.settings =viridisTheme(region = viridis(10)),#do pacote trellis
          main=list('Mapas', col='red'),
          xlab=list('Longitude',  fontface='bold'),
          ylab=list('Latitude', rot=90, fontface='bold')
          ) 
```




Usefull links:
To ggplot themes: <https://ggplot2.tidyverse.org/reference/ggtheme.html>
Viridis palettes: <https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html>
RColorBrewer palletes: <http://www.nickeubank.com/wp-content/uploads/2015/10/RGIS3_MakingMaps_part1_mappingVectorData.html>
To sp plots: <https://edzer.github.io/sp/>
To colorspace palletes: <https://cran.r-project.org/web/packages/colorspace/vignettes/colorspace.html>

